Graphics

### 2018-09-12 contest/graphics/graphics.Rmd
graphics updates

```{r, fig.height=4, fig.width=10}

@@

```{r, fig.height=4, fig.width=8, fig.align='center'}

@@

@@

>>>>

```{r, fig.height=4, fig.width=12}

@@

@@

# Pairs

```{r, fig.height=12, fig.width=12}
library(GGally)

vars <- c("ht", "age", "rank", "opponent_rank", "ace", "df", "svpt", "1stIn", "SvGms", "bpSaved",
          "bpFaced", "pointswon", "gameswon")

ggpairs(gs_players,
        columns = which(names(gs_players) %in% vars),
        mapping=ggplot2::aes(colour = factor(did_win)))

## Follow-up

```{r, fig.height=3, fig.width=4}
ggplot(gs_players) + geom_point(aes(log(ht+1), log(ace+1), color = factor(did_win)))
```

@@

```{r}
gs_num <- select(gs, w_ace, w_df, w_svpt, w_1stIn,
                w_bpSaved, w_bpFaced) %>%
na.omit()

mds$tournament <- select(gs, w_ace, w_df, w_svpt, w_1stIn,
                w_bpSaved, w_bpFaced, tournament) %>%
na.omit() %>% pull( tournament)
